Data Pre-Processing/Cleaning Script

### 2023-03-16 code/analysis_code/exploratory_analysis.qmd
statistical_analysis_code

```{r}
# Time vs Hospitalizations
ggplot(training_data_final %>% 
         group_by(Year, Pathogen_Type, Hospitalizations) %>% 
         count() %>% 
         mutate(true_hospitalization = n * Hospitalizations), aes(x = Year, y = true_hospitalization, group = Pathogen_Type, color = Pathogen_Type)) + geom_point() + 
  geom_jitter() + 
  labs(x = "Year", y = "Hospitalizations", title = "Scatter Plot of Hospitalizations by Year and Pathogen Type")

@@

>>>>

```{r fig.height=8,fig.width=8}
# Time vs Hospitalizations
ggplot(training_data_final %>% 
         group_by(Year, Pathogen_Type, Hospitalizations) %>% 
         count() %>% 
         mutate(true_hospitalization = n * Hospitalizations), aes(x = Year, y = true_hospitalization, group = Pathogen_Type, color = Pathogen_Type)) + geom_point() + 
  geom_jitter() + 
  labs(x = "Year", y = "Hospitalizations", title = "Scatter Plot of Hospitalizations by Year and Pathogen Type")

@@

####

Norovirus_Hosp=training_data_final%>%
  select(Simplified_Etiology, Hospitalizations, `IFSAC Category`)%>%
  group_by(Simplified_Etiology, Hospitalizations, `IFSAC Category`)%>%
  filter(Simplified_Etiology=="Salmonella")%>%
  filter(`IFSAC Category`!= %n% C("Multiple","Other"))%>%
  count()%>%
  mutate(total_hospitalizations=n*Hospitalizations)

ggplot(Norovirus_Hosp,aes(x=`IFSAC Category`,y=total_hospitalizations))+
  geom_boxplot()+
  scale_x_discrete(guide=guide_axis(n.dodge=3))

### 2023-03-16 code/processing_code/processingfile_v1.qmd
statistical_analysis_code

data_location <- here(
  "data","raw_data","NationalOutbreakPublicDataTool.xlsx")
testing_data <- readxl::read_excel(data_location)
```

@@

## Testing Data
```{r}
str(analysis_data)
summary(analysis_data)

>>>>

data_location <- here(
  "data","raw_data","NationalOutbreakPublicDataTool.xlsx")
analysis_data <- readxl::read_excel(data_location)
```

@@

## Analysis Data
```{r}
str(analysis_data)
summary(analysis_data)
